Notes

### 2020-05-25 Notes/Notes.tex

To include the decoherence effects, we solve for master equation in Lindblad form
\begin{align}
  \partial_t \rho (t) = - \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $L_j$ are the Lindblad operators for decoherence. In this study we only include lowest order approximation, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma=1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time.

>>>>

To include the decoherence effects, we solve for master equation in Lindblad form
\begin{align}
  \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $L_j$ are the Lindblad operators for decoherence. In this study we only include lowest order approximation, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma=1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time.

The Lindblad master equation from full counting statistics is given by (arXiv:1312.3476 [quant-ph])
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_{\mu>\nu,x\in \pm} (2L^x_{\mu \nu} \rho(t) L_{\mu \nu}^{x\dagger} - \{ L^{x\dagger}_{\mu \nu} L^x_{\mu \nu}, \rho(t) \}) ,
\end{align}
and
\begin{align}
  L^-_{\mu \nu}=(\sqrt{\gamma}) a_{\mu \nu} \\
  L^+_{\mu \nu}=(\sqrt{\gamma p_{\mu \nu}} )a_{\mu \nu}^\dagger ,
\end{align}
, where indices $\mu$ and $\nu$ run through all pairs of the many-body eigenstates of the system Hamiltonian for $\mu > \nu$ and $E_0 \le E_1 \le ... \le E_{dim(\mbox{Hilbert space})}$. $p_{\mu \nu}=e^{-\beta (E_\mu-E_\nu)}$. $a_{\mu \nu}=|\nu \rangle \langle \mu |$ is the lowering operator for many-body eigen states in the qubits system.
